Behavior Driven Development in Haskell

### 2012-05-22 paper.tex
structuring a paper.

\usepackage{amsmath}
\usepackage{enumerate}

@@

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Title Text}
\subtitle{Subtitle Text, if any}

\authorinfo{Name1}
           {Affiliation1}
           {Email1}
\authorinfo{Name2\and Name3}
           {Affiliation2/3}
           {Email2/3}

@@

\begin{abstract}
This is the text of the abstract.
\end{abstract}

@@

\keywords
keyword1, keyword2

@@

\input{main.tex}

\appendix
\section{Appendix Title}

This is the text of the appendix, if you need one.

@@

Acknowledgments, if needed.

>>>>

\usepackage{amsmath}

@@

\titlebanner{A draft paper to be submitted to Haskell Symposium 2012}
\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Behavior Driven Development in Haskell}
%\subtitle{Subtitle Text, if any}

\authorinfo{Simon HENGEL}
           {TBD: Affiliation}
           {TBD: Email}
\authorinfo{Trystan SPANGLER}
           {TBD: Affiliation}
           {TBD: Email}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

\begin{abstract}
TBD: This is the text of the abstract.
\end{abstract}

@@

\keywords
software design, documentation, automatic test

@@

The text of the paper begins here.

The contribution of this paper is as follows:

\begin{itemize}
\item Introduced doctest from Python community to Haskell community
\item Introduced *spec from Ruby community to Haskell community
\item Integrated doctest and QuickCheck
\item Show best current practice of design/documentation/tests
\end{itemize}

\section{Observation}

Should talk about equation property.

\section{Solution}

Note: Kazu defines functions without signatures if they are simple enough.
And their signatures are automatically inserted by IDE (like ghc-mod) later.

\section{Implementation}

\subsection{doctest}

\subsection{doctest and QuickCheck}

\subsection{hspec}

\section{Conclusion}

%% \appendix
%% \section{Appendix Title}

%% This is the text of the appendix, if you need one.

@@

TBD: Acknowledgments, if needed.
